Hyperparameter Learning \\ for Conditional Mean Embeddings \\ with Rademacher Complexity Bounds : \\ Supplementary Material

### 2018-04-02 ECML2018/paper/mce_appendix_ecml2018.tex
Convert paper and appendix to ECML format

\documentclass{article}

% if you need to pass options to natbib, use, e.g.:
% \PassOptionsToPackage{numbers, compress}{natbib}
% before loading nips_2017
%
% to avoid loading the natbib package, add option nonatbib:
% \usepackage[nonatbib]{nips_2017}

\usepackage{nips_2017}

% to compile a camera-ready version, add the [final] option, e.g.:
% \usepackage[final]{nips_2017}

% My Packages
\usepackage[nokeyprefix]{refstyle}
\usepackage{varioref}
\usepackage{xr-hyper}
\externaldocument[cake]{cake}
% End My Packages

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage[colorlinks=true,linkcolor=green,citecolor=cyan]{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography

% My Packages
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{mathbbol}
\usepackage{mathtools}
\usepackage{mathrsfs}
\usepackage{vector}
\usepackage{cleveref}
\usepackage{bm}
\usepackage[dvipsnames]{xcolor}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{claim}[theorem]{Claim}
\usepackage{multirow}
\usepackage{algorithm}
\usepackage{algorithmic}
\newcommand{\argmax}{\operatornamewithlimits{argmax}}
\numberwithin{equation}{section}
\numberwithin{table}{section}
\numberwithin{algorithm}{section}

@@

\title{CAKE: Classification \textit{avec} Kernel Embeddings \\ using Rademacher Complexity Bounds: \\ Supplementary Material}

\author{
}

@@

	\section{Convergence Theorems for Kernel Embedding Classifiers}
	\label{app:convergence_theorems}

	In this section we provide theorems and derivations that establish convergence properties of kernel embedding classifiers.

	We consider the case in which a dataset, represented by the collection of random variables $\{X_{i}, Y_{i}\}_{i = 1}^{n}$ where $X_{i} : \Omega \to \mathcal{X}$,  $Y_{i} : \Omega \to \mathcal{Y}$ for all $i \in \mathbb{N}_{n}$, is collected in a \textit{iid} fashion from some distribution $\mathbb{P}_{X Y}$. That is $\{X_{i}, Y_{i}\} \sim \mathbb{P}_{X Y}$ for all $i \in \mathbb{N}_{n}$ and each observed sample is independent from each other. Suppose we have an estimator function $\hat{f}^{(n)} : \mathcal{X} \to \mathbb{R}$ which is to estimate some target function  $f : \mathcal{X} \to \mathbb{R}$, usually but not necessarily derived from $\mathbb{P}_{Y |X }$, empirically using the collected dataset $\{X_{i}, Y_{i}\}_{i = 1}^{n}$ of size $n \in \mathbb{N}_{+}$. Here, we use the superscript $(n)$ to denote the estimator's dependence on the dataset. From this point on, we drop this superscript to avoid cluttered notation. However, one should keep in mind that $\hat{f}$ is estimated using the dataset $\{X_{i}, Y_{i}\}_{i = 1}^{n}$ and is thus random over the possible data observation events $\omega \in \Omega$. We would like to provide a sense of the stochastic convergence of $\hat{f}$ to $f$ by providing an upper bound of their absolute pointwise difference $| \hat{f}(x) - f(x) |$, and show that such an upper bound converges to zero at some stochastic rate. Since the kernel embedding classifier is based on conditional embeddings (and, as we will show, is equivalent to a conditional embedding), this upper bound will be provided by the RKHS norm of the error between empirical and true conditional embeddings. Specifically, the empirical conditional embedding stochastically converges to the true conditional embedding $\mu_{Y | X = x}$ in the RKHS norm at a rate of $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$, under the assumption that $k(x, \cdot)$ is in the image of $C_{XX}$ \cite[Theorem 6]{song2009hilbert}. That is,
	\begin{equation}
	\forall x \in \mathcal{X}, \; \epsilon > 0, \; \exists M_{\epsilon} > 0 \quad s.t. \quad \mathbb{P}\Big[\big\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \big\|_{\mathcal{H}_{l}} > M_{\epsilon} \Big((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}}\Big)\Big] < \epsilon.
	\label{eq:empirical_conditional_embedding_stochastic_convergence}
	\end{equation}

	\begin{theorem}[Pointwise and Uniform Convergence of Estimators based on Conditional Embeddings]
		\label{thm:pointwise_uniform_convergence}
		Suppose that $k(x, \cdot)$ is in the image of $C_{XX}$ and that there exists $0 \leq \gamma(x) < \infty$ such that for some estimator function $\hat{f} : \mathcal{X} \to \mathbb{R}$ and target function  $f : \mathcal{X} \to \mathbb{R}$,

@@

	With \cref{thm:pointwise_uniform_convergence}, we can now show the convergence of various estimators based on the conditional embedding, as long as we can show that their estimator error is upper bounded by a multiple of the conditional embedding error in the RKHS norm. As such, we turn to the convergence of the empirical decision probability function \eqref[name= , xr=cake]{eq:empirical_decision_probability} below.

@@

			From \eqref[name = , xr=cake]{eq:indicator_function}, since $\mathbb{1}_{c} = \delta(c, \cdot)$ and using the fact that $\delta$ is a reproducing kernel, we have that for all $c \in \mathcal{Y} = \mathbb{N}_{m}$.
			\begin{equation}
			\begin{aligned}
			\big\| \mathbb{1}_{c} \big\|_{\mathcal{H}_{\delta}}^{2} = \langle \mathbb{1}_{c}, \mathbb{1}_{c} \rangle = \langle \delta(c, \cdot), \delta(c, \cdot) \rangle = \delta(c, c) = 1.
			\label{eq:indicator_rkhs_norm}
			\end{aligned}
			\end{equation}

@@

	The above proof is for uniform convergence over all $x \in \mathcal{X}$ at the stochastic rate of at least $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$. Intuitively, however, for stationary zero-centred kernels like the Gaussian kernel, the convergence rate may be higher at regions of high data density, since the kernel effects, being centred around the training data, are stronger at these regions. The worse case convergence rate described here in the theorem would be a tight lower bound for regions in $\mathcal{X}$ with lower data density, where the kernel effects have decayed and most empirical probabilities are smaller and further from summing up to one.

	Because the label space $\mathcal{Y} = \mathbb{N}_{m}$ is discrete and finite, \textit{bounded} functions $g \in \mathcal{H}_{\delta}$ in the RKHS are actually equivalent to their vector representations $\bvec{g} := \{g(c)\}_{c = 1}^{m}$, because one can always write $g = \sum_{c = 1}^{m} g(c) \delta(c, \cdot)$. This immediately implies that inner products in this space are simply the usual dot products in a Euclidean space, since

@@

	Consequently, the RKHS norm for bounded functions $g \in \mathcal{H}_{\delta}$ is simply the $\ell_{2}$-norm of its vector representation $\bvec{g}$,

	\begin{equation}
	\lVert g \rVert_{\mathcal{H}_{\delta}} = \lVert \bvec{g} \rVert_{\ell_{2}}.
	\label{eq:rkhs_norm_is_l2_norm}
	\end{equation}

@@

			Since indicator functions are the canonical features of the label RKHS $\mathcal{H}_{\delta}$, we employ the fact that expectations of indicator functions are probabilities to prove this claim,

@@

	\Cref{thm:empirical_probability_is_embedding} shows that the decision function $\bvec{f}(x)$ \eqref[name = , xr=cake]{eq:empirical_decision_probability_vector} of a kernel embedding classifier is no more than the empirical conditional embedding estimated from the data.

@@

		\begin{proof}
			For convergence in $\ell_{1}$, we simply extend \cref{thm:probability_convergence}, which proved that each entry of $\hat{\bvec{p}}(x)$ converges pointwise uniformly at a rate of $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$ to the corresponding entry of $\bvec{p}(x)$. Since each entry converges stochastically at a rate of $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$, then so does the entire vector. More formally, from \eqref[name = ]{eq:decision_probability_error_upper_bound} and \eqref[name = ]{eq:indicator_rkhs_norm}, the $\ell_{1}$-norm of the difference can be bounded,

@@

			For convergence in $\ell_{2}$, we show that the $\ell_{2}$-norm of the difference between the true and empirical decision probability vector functions is the same as the RKHS norm of the difference between the true and empirical conditional embedding, which converges to zero at a stochastic rate of at least $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$ for all $x \in \mathcal{X}$ and $c \in \mathcal{Y} = \mathbb{N}_{m}$ by \eqref[name = ]{eq:empirical_conditional_embedding_stochastic_convergence}. To this end, we use \cref{thm:probability_is_embedding} and \cref{thm:empirical_probability_is_embedding} and write

@@

			where the last equality comes from \eqref[name = ]{eq:rkhs_norm_is_l2_norm} and the fact that the empirical and true conditional embeddings are bounded functions in the RKHS. Again, by \cref{thm:pointwise_uniform_convergence} with $\gamma(x) = 1$ independent of $x \in \mathcal{X}$, we have uniform convergence in $\ell_{2}$.
		\end{proof}
	\end{lemma}

	\subsection{Information Entropy of Kernel Embedding Classifiers}
	\label{app:information_entropy}

		The kernel embedding classifier provides decision probabilities instead of just a single label prediction. Such a probabilistic classifier allows us to quantify the uncertainty of its predictions for any given example $x \in \mathcal{X}$ through the information entropy \citep{shannon1951prediction, jaynes1957information}. This is ideal for detecting the decision boundaries of the classifier and areas of low data density.

@@

		The first approach is straight forward, which involves simply computing the information entropy with the clip normalised probabilities \eqref[name = , xr=cake]{eq:empirical_decision_probability_clip_normalised}, at the query point $x \in \mathcal{X}$,

		\begin{equation}
			\tilde{h}(x) := - \sum_{c = 1}^{m} \tilde{p}_{c}(x) \log{\tilde{p}_{c}(x)}.
		\label{eq:entropy_clip_normalise}
		\end{equation}

		We call \eqref[name = ]{eq:entropy_clip_normalise} the \textit{clip-normalised information entropy}. Since $\tilde{p}_{c}(x)$ converges pointwise to $p_{c}(x)$ with increasing data, $\tilde{h}(x)$ also converges pointwise to $h(x)$.

		Just as decision probabilities can be expressed as an expectation of indicator functions, information entropy can be expressed as expected information,
		\begin{equation}
			\begin{aligned}
				\mathbb{H}[Y | X = x] &= - \sum_{c = 1}^{m} \mathbb{P}[Y = c| X = x] \log{\mathbb{P}[Y = c | X = x]} \\
				&= \mathbb{E}[- \log{\mathbb{P}[Y | X = x]} | X = x] \\
				&= \mathbb{E}[u_{x}(Y) | X = x],
			\end{aligned}
		\end{equation}
		where $u_{x}(y) := - \log{\mathbb{P}[Y = y | X = x]}$ is the \textit{information} (in nats) we would gain when we discover that example $x$ actually has label $y$. Note that while $\mathbb{P}[Y = c | X = x]$ is a constant, we employ the shorthand notation $\mathbb{P}[Y| X = x]$ for the random variable $g(Y)$ where $g(y) := \mathbb{P}[Y = y | X = x]$. If $u_{x} : \mathbb{N}_{m} \to \mathbb{R}$ is in the RKHS $\mathcal{H}_{\delta}$, then we know that this expectation can also be approximated by $\langle \hat{\mu}_{Y | X = x}, u_{x} \rangle$. This is the basis of our second approach.

		Assuming that $\mathbb{P}[Y = y | X = x]$ is never exactly zero for all labels $y \in \mathcal{Y}$ and examples $x \in \mathcal{X}$, then $u_{x}(y)$ is bounded on its discrete domain $\mathbb{N}_{m}$. We can thus write $u_{x} = \sum_{c = 1}^{m} - \log{\mathbb{P}[Y = c | X = x]} \delta(c, \cdot)$ which shows that $u_{x}$ is in the span of the canonical kernel features and is thus in the RKHS. Hence, similar to the case with decision probabilities, with $u_{x} \in \mathcal{H}_{\delta}$ and $\bvec{u}_{x} := \{u_{x}(y_{i})\}_{i = 1}^{n}$ we let $g = u_{x}$ in \eqref[name = , xr=cake]{eq:empirical_conditional_expectation} and estimate $h(x)$ by

@@

				where the we used the triangle inequality and Cauchy Schwarz inequality in a Hilbert space respectively. Since $l = \delta$ is bounded, so is $\hat{\mu}_{Y | X = x}(c) = \sum_{i = 1}^{n} w_{i} \delta(y_{i}, c)$ for some embedding weights $w_{i}$ and all $c \in \mathbb{N}_{m}$, and thus its RKHS norm is finite for all $n \in \mathbb{N}_{n}$. Similarly, assuming that $p_{c}(x)$ is never exactly zero, $u_{x}(c)$ is also finite for all $c \in \mathbb{N}_{m}$ and thus so is its RKHS norm. We already know that $\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \|_{\mathcal{H}_{\delta}}$ stochastically converges to zero at the rate $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$ \eqref[name = ]{eq:empirical_conditional_embedding_stochastic_convergence}. Thus, it remains to bound $\| \hat{u}_{x} - u_{x} \|_{\mathcal{H}_{\delta}}$ by a multiple of $\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \|_{\mathcal{H}_{\delta}}$.

@@

				where we define $\alpha_{x} := \max_{c \in \mathbb{N}_{m}} \frac{1}{| \mu_{Y | X = x}(c) |}$, which is well defined as the conditional embedding is bounded. Since the RKHS norm of bounded functions in $\mathcal{H}_{\delta}$ is simply the $\ell_{2}$-norm of their vector representations \eqref[name = ]{eq:rkhs_norm_is_l2_norm}, we have

@@

\newpage
\section{Learning Theoretic Bounds for Kernel Embedding Classifiers}
\label{app:learning_theoretic_bounds}

	In this section we derive Rademacher complexity bounds for kernel embedding classifiers, and show that it can be used in conjunction with cross entropy loss to bound the expected risk with high probability.

@@

		Suppose a set of training data $\{x_{i}, y_{i}\}_{i = 1}^{n}$ is drawn from $\mathbb{P}_{X Y}$ in an \textit{iid} fashion. We denote the one hot encoded target labels of $\{y_{i}\}_{i = 1}^{n}$ by $\bvec{y}_{i} := \{\mathbb{1}_{c}(y_{i})\}_{c = 1}^{m} \in \{0, 1\}^{m}$ and $\bvec{Y} := \begin{bmatrix} \bvec{y}_{1} & \bvec{y}_{2} & \cdots & \bvec{y}_{n} \end{bmatrix}^{T} \in \{0, 1\}^{n \times m}$. Similarly, let $\bvec{y} \in \{0, 1\}^{m}$ denote the one hot encoded target labels for a generic label $y \in \mathcal{Y}$. Let $k_{\theta} : \mathcal{X} \times \mathcal{X} \to [0, \infty)$ be a family of positive definite kernels indexed by $\theta \in \Theta$. As before, we define the shorthand notation for the gram matrices $K_{\theta} := \{k_{\theta}(x_{i}, x_{j}) : i \in \mathbb{N}_{n}, j \in \mathbb{N}_{n}\}$ and $\bvec{k}_{\theta}(x) := \{k_{\theta}(x_{i}, x) : i \in \mathbb{N}_{n}\}$, and $\lambda$ denotes the regularisation parameter of the conditional embedding \eqref[name = , xr=cake]{eq:empirical_conditional_embedding}. The kernel embedding classifier has a predictor form $\hat{\bvec{p}}(x) = \bvec{f}_{\theta, \lambda}(x)$ \eqref[name = , xr=cake]{eq:empirical_decision_probability_vector} defined by

@@

		where each entry of the predictor $\bvec{f}_{\theta, \lambda}(x)$ is the decision probability estimate for $p_{c}(x)$. This defines the function class of the predictor over the kernel family and a set of regularisation parameters for any set of training observations $\{x_{i}, y_{i}\}_{i = 1}^{n}$,

>>>>

% This is LLNCS.DEM the demonstration file of
% the LaTeX macro package from Springer-Verlag
% for Lecture Notes in Computer Science,
% version 2.4 for LaTeX2e as of 16. April 2010
%
\documentclass{llncs}
%
\usepackage{makeidx}  % allows for indexgeneration

\bibliographystyle{apalike}  % Use the "unsrtnat" BibTeX style for formatting the Bibliography
\usepackage[square, authoryear, comma, sort&compress]{natbib}  % Use the "Natbib" style for the references in the Bibliography

% My Packages
\usepackage{glossaries}
\usepackage[nokeyprefix]{refstyle}
\usepackage{varioref}
\usepackage{xr-hyper}
\externaldocument[mce_ecml2018]{mce_ecml2018}
% End My Packages

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage[colorlinks=true,linkcolor=black,citecolor=black]{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography

% My Packages
\usepackage{amsmath}
\usepackage{amssymb}
%\usepackage{amsthm}
\usepackage{mathbbol}
\usepackage{mathtools}
\usepackage{mathrsfs}
\usepackage{vector}
\usepackage{cleveref}
\usepackage{bm}
\usepackage[dvipsnames]{xcolor}
%\newtheorem{theorem}{Theorem}[section]
%\newtheorem{corollary}[theorem]{Corollary}
%\newtheorem{lemma}[theorem]{Lemma}
%\newtheorem{claim}[theorem]{Claim}
\usepackage{multirow}
\usepackage{algorithm}
\usepackage{algorithmic}
\newcommand{\argmax}{\operatornamewithlimits{argmax}}
\numberwithin{equation}{section}
\numberwithin{table}{section}
\numberwithin{algorithm}{section}

\newacronym{CME}{CME}{conditional mean embedding}
\newacronym{MCE}{MCE}{multi-categorical conditional embedding}
\newacronym{CEN}{CEN}{conditional embedding network}
\newacronym{RKHS}{RKHS}{reproducing kernel Hilbert space}
\newacronym{SVM}{SVM}{support vector machine}
\newacronym{SVC}{SVC}{support vector classifier}
\newacronym{GP}{GP}{Gaussian process}
\newacronym{GPs}{GPs}{Gaussian processes}
\newacronym{GPC}{GPC}{Gaussian process classifier}
\newacronym{KRR}{KRR}{kernel ridged regressor}
\newacronym{RLSC}{RLSC}{regularized least squares classification}
\newacronym{ERM}{ERM}{empirical risk minimization}
\newacronym{MMD}{MMD}{maximum mean discrepancy}
\newacronym{RCB}{RCB}{Rademacher complexity bound}
\newacronym{OVA}{OVA}{one versus all}
\newacronym{CNN}{CNN}{convolutional neural network}

@@

\title{Hyperparameter Learning \\ for Conditional Mean Embeddings \\ with Rademacher Complexity Bounds : \\ Supplementary Material}

\titlerunning{Hyperparameter Learning for Conditional Mean Embeddings}
% abbreviated title (for running head), also used for the TOC unless \toctitle is used

\author{Kelvin Hsu \inst{1, 2} \and
	Richard Nock \inst{1, 2, 3} \and
	Fabio Ramos \inst{1, 2}}
%
\authorrunning{Hsu et. al.} % abbreviated author list (for running head)
%
%%%% list of authors for the TOC (use if author list has to be modified)
\tocauthor{Kelvin Hsu, Richard Nock, Fabio Ramos}
%
\institute{	University of Sydney, Sydney, Australia, \\ \and
	Data61, CSIRO, Sydney, Australia \\ \and
	Australian National University, Canberra, Australia}

@@

	\section{Convergence Theorems for Multi-Categorical Conditional Mean Embeddings}
	\label{app:convergence_theorems}

	In this section we provide theorems and derivations that establish convergence properties of \glspl{MCE}. Most of the convergence results hold due to \glspl{MCE} being special cases of \glspl{CME}, whose empirical estimates are known to converge. We include this section for completeness.

	Suppose $\{X_{i}, Y_{i}\} \sim \mathbb{P}_{X Y}$ are \textit{iid} for all $i \in \mathbb{N}_{n}$, with $X_{i} : \Omega \to \mathcal{X}$ and $Y_{i} : \Omega \to \mathcal{Y}$. We wish to estimate some target function $f : \mathcal{X} \to \mathbb{R}$ by $\hat{f} : \mathcal{X} \to \mathbb{R}$ empirically with a dataset $\{X_{i}, Y_{i}\}_{i = 1}^{n}$ of size $n \in \mathbb{N}_{+}$. Since $\hat{f}$ is empirically estimated, it is a random function over the possible data observation events $\omega \in \Omega$. The aim is to provide a sense of the stochastic convergence of $\hat{f}$ to $f$ by providing an upper bound of their absolute pointwise difference $| \hat{f}(x) - f(x) |$, and show that such an upper bound converges to zero at some stochastic rate. Such an upper bound is provided by the convergence properties of \glspl{CME}. In particular, the empirical \gls{CME} stochastically converges to the \gls{CME} at rate $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$, under the assumption that $k(x, \cdot) \in \mathrm{image}(C_{XX})$ \cite[Theorem 6]{song2009hilbert}. That is,
	\begin{equation}
	\forall x \in \mathcal{X}, \; \epsilon > 0, \; \exists M_{\epsilon} > 0 \quad s.t. \quad \mathbb{P}\Big[\big\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \big\|_{\mathcal{H}_{l}} > M_{\epsilon} \Big((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}}\Big)\Big] < \epsilon.
	\label{eq:empirical_conditional_embedding_stochastic_convergence}
	\end{equation}
	In practice, the assumption that $k(x, \cdot) \in \mathrm{image}(C_{XX})$ can be relaxed by replacing $\mathcal{U}_{Y | X} = C_{YX} C_{XX}^{-1}$ with $\mathcal{U}_{Y | X} = C_{YX} (C_{XX} + \lambda I)^{-1}$ \citep{song2013kernel}. This will apply to all the subsequent theorems in this section.
	\begin{theorem}[Pointwise and Uniform Convergence of Estimators based on Conditional Embeddings]
		\label{thm:pointwise_uniform_convergence}
		Suppose that $k(x, \cdot)$ is in the image of $C_{XX}$ and that there exists $0 \leq \gamma(x) < \infty$ such that for some estimator function $\hat{f} : \mathcal{X} \to \mathbb{R}$ and target function  $f : \mathcal{X} \to \mathbb{R}$,

@@

	With \cref{thm:pointwise_uniform_convergence}, we can now show the convergence of various estimators based on the conditional embedding, as long as we can show that their estimator error is upper bounded by a multiple of the conditional embedding error in the \gls{RKHS} norm. As such, we turn to the convergence of the empirical decision probability function \eqref[name= , xr=cake]{eq:empirical_decision_probability} below.

@@

			Since $\mathbb{1}_{c} = \delta(c, \cdot)$ and using the fact that $\delta$ is a reproducing kernel, we have that for all $c \in \mathcal{Y} = \mathbb{N}_{m}$.
			\begin{equation}
			\begin{aligned}
			\big\| \mathbb{1}_{c} \big\|_{\mathcal{H}_{\delta}}^{2} = \langle \mathbb{1}_{c}, \mathbb{1}_{c} \rangle = \langle \delta(c, \cdot), \delta(c, \cdot) \rangle = \delta(c, c) = 1.
			\label{eq:indicator_RKHS_norm}
			\end{aligned}
			\end{equation}

@@

	The above proof is for uniform convergence over all $x \in \mathcal{X}$ at the stochastic rate of at least $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$. Intuitively, however, for stationary zero-centered kernels like the Gaussian kernel, the convergence rate may be higher at regions of high data density, since the kernel effects, being centered around the training data, are stronger at these regions. The worse case convergence rate described here in the theorem would be a tight lower bound for regions in $\mathcal{X}$ with lower data density, where the kernel effects have decayed and most empirical probabilities are smaller and further from summing up to one.

	Because the label space $\mathcal{Y} = \mathbb{N}_{m}$ is discrete and finite, \textit{bounded} functions $g \in \mathcal{H}_{\delta}$ in the \gls{RKHS} are equivalent to their vector representations $\bvec{g} := \{g(c)\}_{c = 1}^{m}$, because one can always write $g = \sum_{c = 1}^{m} g(c) \delta(c, \cdot)$. In other words, there is an isomorphism between $\mathbb{H}_{\delta}$ and $\mathbb{R}^{m}$. A convenient consequence is that inner products in the \gls{RKHS} are simply the usual dot products in a Euclidean space, since

@@

	Consequently, the \gls{RKHS} norm for bounded functions $g \in \mathcal{H}_{\delta}$ is simply the $\ell_{2}$-norm of its vector representation $\bvec{g}$,

	\begin{equation}
	\lVert g \rVert_{\mathcal{H}_{\delta}} = \lVert \bvec{g} \rVert_{\ell_{2}}.
	\label{eq:RKHS_norm_is_l2_norm}
	\end{equation}

@@

			Since indicator functions are the canonical features of the label \gls{RKHS} $\mathcal{H}_{\delta}$, we employ the fact that expectations of indicator functions are probabilities to prove this claim,

@@

	\Cref{thm:empirical_probability_is_embedding} shows that the decision function $\bvec{f}(x)$ \eqref[name = , xr=cake]{eq:empirical_decision_probability_vector} of a \gls{MCE} is no more than the empirical conditional embedding estimated from the data.

@@

		\begin{proof}
			For convergence in $\ell_{1}$, we simply extend \cref{thm:probability_convergence}, which proved that each entry of $\hat{\bvec{p}}(x)$ converges pointwise uniformly at a rate of $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$ to the corresponding entry of $\bvec{p}(x)$. Since each entry converges stochastically at a rate of $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$, then so does the entire vector. More formally, from \eqref[name = ]{eq:decision_probability_error_upper_bound} and \eqref[name = ]{eq:indicator_RKHS_norm}, the $\ell_{1}$-norm of the difference can be bounded,

@@

			For convergence in $\ell_{2}$, we show that the $\ell_{2}$-norm of the difference between the true and empirical decision probability vector functions is the same as the \gls{RKHS} norm of the difference between the true and empirical conditional embedding, which converges to zero at a stochastic rate of at least $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$ for all $x \in \mathcal{X}$ and $c \in \mathcal{Y} = \mathbb{N}_{m}$ by \eqref[name = ]{eq:empirical_conditional_embedding_stochastic_convergence}. To this end, we use \cref{thm:probability_is_embedding} and \cref{thm:empirical_probability_is_embedding} and write

@@

			where the last equality comes from \eqref[name = ]{eq:RKHS_norm_is_l2_norm} and the fact that the empirical and true conditional embeddings are bounded functions in the \gls{RKHS}. Again, by \cref{thm:pointwise_uniform_convergence} with $\gamma(x) = 1$ independent of $x \in \mathcal{X}$, we have uniform convergence in $\ell_{2}$.
		\end{proof}
	\end{lemma}

	\subsection{Information Entropy of \glspl{MCE}}
	\label{app:information_entropy}

	The \gls{MCE} provides decision probabilities instead of just a single label prediction. Such a probabilistic classifier allows us to quantify the uncertainty of its predictions for any given example $x \in \mathcal{X}$ through the information entropy \citep{shannon1951prediction, jaynes1957information}. This is ideal for detecting the decision boundaries of the classifier and areas of low data density.

@@

	The first approach is straight forward, which involves simply computing the information entropy with the clip normalized probabilities \eqref[name = , xr=cake]{eq:empirical_decision_probability_clip_normalized}, at the query point $x \in \mathcal{X}$,

	\begin{equation}
	\tilde{h}(x) := - \sum_{c = 1}^{m} \tilde{p}_{c}(x) \log{\tilde{p}_{c}(x)}.
	\label{eq:entropy_clip_normalize}
	\end{equation}

	We call \eqref[name = ]{eq:entropy_clip_normalize} the \textit{clip-normalized information entropy}. Since $\tilde{p}_{c}(x)$ converges pointwise to $p_{c}(x)$ with increasing data, $\tilde{h}(x)$ also converges pointwise to $h(x)$.

	Just as decision probabilities can be expressed as an expectation of indicator functions, information entropy can be expressed as expected information,
	\begin{equation}
	\begin{aligned}
	\mathbb{H}[Y | X = x] &= - \sum_{c = 1}^{m} \mathbb{P}[Y = c| X = x] \log{\mathbb{P}[Y = c | X = x]} \\
	&= \mathbb{E}[- \log{\mathbb{P}[Y | X = x]} | X = x] \\
	&= \mathbb{E}[u_{x}(Y) | X = x],
	\end{aligned}
	\end{equation}
	where $u_{x}(y) := - \log{\mathbb{P}[Y = y | X = x]}$ is the \textit{information} (in nats) we would gain when we discover that example $x$ actually has label $y$. Note that while $\mathbb{P}[Y = c | X = x]$ is a constant, we employ the shorthand notation $\mathbb{P}[Y| X = x]$ for the random variable $g(Y)$ where $g(y) := \mathbb{P}[Y = y | X = x]$. If $u_{x} : \mathbb{N}_{m} \to \mathbb{R}$ is in the \gls{RKHS} $\mathcal{H}_{\delta}$, then we know that this expectation can also be approximated by $\langle \hat{\mu}_{Y | X = x}, u_{x} \rangle$. This is the basis of our second approach.

	Assuming that $\mathbb{P}[Y = y | X = x]$ is never exactly zero for all labels $y \in \mathcal{Y}$ and examples $x \in \mathcal{X}$, then $u_{x}(y)$ is bounded on its discrete domain $\mathbb{N}_{m}$. We can thus write $u_{x} = \sum_{c = 1}^{m} - \log{\mathbb{P}[Y = c | X = x]} \delta(c, \cdot)$ which shows that $u_{x}$ is in the span of the canonical kernel features and is thus in the \gls{RKHS}. Hence, similar to the case with decision probabilities, with $u_{x} \in \mathcal{H}_{\delta}$ and $\bvec{u}_{x} := \{u_{x}(y_{i})\}_{i = 1}^{n}$ we let $g = u_{x}$ in \eqref[name = , xr=cake]{eq:empirical_conditional_expectation} and estimate $h(x)$ by

@@

			where the we used the triangle inequality and Cauchy Schwarz inequality in a Hilbert space respectively. Since $l = \delta$ is bounded, so is $\hat{\mu}_{Y | X = x}(c) = \sum_{i = 1}^{n} w_{i} \delta(y_{i}, c)$ for some embedding weights $w_{i}$ and all $c \in \mathbb{N}_{m}$, and thus its \gls{RKHS} norm is finite for all $n \in \mathbb{N}_{n}$. Similarly, assuming that $p_{c}(x)$ is never exactly zero, $u_{x}(c)$ is also finite for all $c \in \mathbb{N}_{m}$ and thus so is its \gls{RKHS} norm. We already know that $\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \|_{\mathcal{H}_{\delta}}$ stochastically converges to zero at the rate $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$ \eqref[name = ]{eq:empirical_conditional_embedding_stochastic_convergence}. Thus, it remains to bound $\| \hat{u}_{x} - u_{x} \|_{\mathcal{H}_{\delta}}$ by a multiple of $\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \|_{\mathcal{H}_{\delta}}$.

@@

			where we define $\alpha_{x} := \max_{c \in \mathbb{N}_{m}} \frac{1}{| \mu_{Y | X = x}(c) |}$, which is well defined as the conditional embedding is bounded. Since the \gls{RKHS} norm of bounded functions in $\mathcal{H}_{\delta}$ is simply the $\ell_{2}$-norm of their vector representations \eqref[name = ]{eq:RKHS_norm_is_l2_norm}, we have

@@

	\newpage
	\section{Learning Theoretic Bounds for Multi-Categorical Conditional Mean Embeddings}
	\label{app:learning_theoretic_bounds}

	In this section we derive \glspl{RCB} for \glspl{MCE}, and show that it can be used in conjunction with cross entropy loss to bound the expected risk with high probability.

@@

	Suppose a set of training data $\{x_{i}, y_{i}\}_{i = 1}^{n}$ is drawn from $\mathbb{P}_{X Y}$ in an \textit{iid} fashion. We denote the one hot encoded target labels of $\{y_{i}\}_{i = 1}^{n}$ by $\bvec{y}_{i} := \{\mathbb{1}_{c}(y_{i})\}_{c = 1}^{m} \in \{0, 1\}^{m}$ and $\bvec{Y} := \begin{bmatrix} \bvec{y}_{1} & \bvec{y}_{2} & \cdots & \bvec{y}_{n} \end{bmatrix}^{T} \in \{0, 1\}^{n \times m}$. Similarly, let $\bvec{y} \in \{0, 1\}^{m}$ denote the one hot encoded target labels for a generic label $y \in \mathcal{Y}$. Let $k_{\theta} : \mathcal{X} \times \mathcal{X} \to [0, \infty)$ be a family of positive definite kernels indexed by $\theta \in \Theta$. As before, we define the shorthand notation for the gram matrices $K_{\theta} := \{k_{\theta}(x_{i}, x_{j}) : i \in \mathbb{N}_{n}, j \in \mathbb{N}_{n}\}$ and $\bvec{k}_{\theta}(x) := \{k_{\theta}(x_{i}, x) : i \in \mathbb{N}_{n}\}$, and $\lambda$ denotes the regularization parameter of the conditional embedding \eqref[name = , xr=cake]{eq:empirical_conditional_embedding}. The \gls{MCE} has a predictor form $\hat{\bvec{p}}(x) = \bvec{f}_{\theta, \lambda}(x)$ \eqref[name = , xr=cake]{eq:empirical_decision_probability_vector} defined by

@@

	where each entry of the predictor $\bvec{f}_{\theta, \lambda}(x)$ is the decision probability estimate for $p_{c}(x)$. This defines the function class of the predictor over the kernel family and a set of regularization parameters for any set of training observations $\{x_{i}, y_{i}\}_{i = 1}^{n}$,
